\documentclass{letter}
\usepackage{hyperref}
\signature{Chris Denniston}
\begin{document}


Although I have no formal research experience I believe this opportunity would be a good way for me to learn. I began programming while I was in high school and, like most young programmers, I wanted to make games. Once I went to college to study Computer Science I began to see the beauty in Math, Computation and Robotics, and I wanted to get more formal and serious in my studies. I began to think about how computers and how data processing could help people. I read through your research projects and they really inspired me because of the impact I could see they would have on the world.

As I mentioned in my other letter I have wanted to pursue further education in machine learning since I became enamored with artificial intelligence and analytics. I have many skills that I think I could apply to the projects. I have worked on the Robotics team for a few years in college and have a pretty strong programming background in Java, Haskell, C\texttt{++} and Python. I have taken a linear algebra course, as well as a machine learning Course, at the University Of Missouri - Kansas City, which I believe will help greatly in the specific projects I have chosen.

I have done analysis of market data at my current employer for Business Intelligence and I have utilized of Kansas City's open government data to do analysis on things I am interested in, specifically microbreweries. I also have utilized the \LaTeX\ typesetting program, which could help in preparing reports.  For these reasons, I think I could be a valuable asset to a research team.

\closing{Thank you for your consideration,}

\end{document}

